### 2015-10-01 paper/main.tex
update paper and figure to v2 of qvalue

\def\lfdr{\text{lfdr}}
\def\lfsr{\text{lfsr}}
\def\x{\mbf{x}}
\def\y{\mbf{y}}
\def\e{\mbf{e}}
\def\g{\mbf{g}}
\def\p{p}
\def\Yb{\hat{Y}_1^{\text{BAYES}}}
\def\Xperp{X_{1 \perp 0}}
\def\Pperp{P_{1 \perp 0}}
\def\Pperpb{\Pperp^{\text{B}}}
\def \hatd { \widehat{ d } }
\def \dhatin {\hatd^{\mbox{\tiny IN}}}
\def \dhatsw {\hatd^{\mbox{\tiny SW}}}
\def \mvn{\text{MVN}}
\def\mn{\text{MN}}
\def \iw{\text{W}^{-1}}
\def \fp {fastPHASE\ }
\def\bhat{\hat{\beta}}
\def\shat{\hat{s}}
\def\var{\rm Var}
\def\mvr{\text{BMVR}}
\def\bfuni{\text{BF}_\text{uni}}
\def\one{\mbf{1}}
\def\zero{\mbf{0}}
\def\hall{H_{\text{all}}}
\def\pall{\p_{\text{all}}}
\def\bfall{\text{BF}_\text{all}}
\def\bfav{\text{BF}_\text{av}}
\def\gall{\gamma_\text{all}}
\def\limbfall{\bfall^\rightarrow}
\def\limbfav{\bfav^\rightarrow}
\def\limbfgamma{\BF_\gamma^\rightarrow}
\def\sxx{S_{xx}}
\def\syy{S_{yy}}
\def\vyy{V_{yy}}
\def\vyx{V_{yx}}
\def\vxx{{V_{xx}}}
\def\rss{\text{\rm RSS}}
\def\dss{\text{\rm $\Delta$SS}}
\def\U{U}
\def\D{D}
\def\I{I}
\def\luu{L_{UU}}
\def\indep{\perp}
\def\qvalue{{\tt qvalue}\xspace}
\def\locfdr{{\tt locfdr}\xspace}
\def\mixfdr{{\tt mixfdr}\xspace}
\def\ashr{{\tt ashr}\xspace}

@@

In addition to these two new ideas, we highlight a third idea that is old, but which remains under-used in practice:
the idea that it may be preferable to focus on estimation rather than on testing.
In principle, Bayesian approaches can naturally unify testing and estimation into a single framework -- testing is
simply estimation with some positive prior probability that the effect is exactly zero.
However, despite ongoing interest in this area from both frequentist \cite{benjamini2005false} and Bayesian \cite{zhao2012empirical,gelman2012we} 
perspectives, in practice large-scale studies that assess many effects almost invariably focus on testing significance and
controlling the FDR, and not on estimation. To help provide a bridge between FDR and estimation we introduce the term
``local false sign rate" (lfsr), which is analogous to the ``local false discovery rate" (lfdr) \cite{efron2008microarrays}, but which measures confidence  
in the {\it sign} of each effect rather than confidence in each effect being non-zero. We show that in some settings, particularly those with many discoveries, 
the lfsr and lfdr can be quite different, and emphasise benefits of the lfsr, particularly its increased robustness to modelling assumptions.

@@

\def\df{df}
\def\FDR{\text{FDR}}
\def\fdr{\text{lfdr}}
\def\FSR{\text{FSR}}
\def\fsr{\text{lfsr}}

@@

% Here we consider one setting in which FDR-based methods are widely used:
%an experimenter has measured a large numbers of ``effects", each with an associated
%measurement precision (standard error), 
%and the goal is to identify which of the effects we can declare to be non-zero, with some prescribed level of confidence.
%Although the usual focus of FDR-based methods is on distinguishing zero and non-zero effects,
%here we also focus on providing estimates -- both point estimates and interval estimates -- for these effects.
%This setting arises commonly in many areas of statistics, and particularly in genomics applications.
%For example, in genomics
%a common goal is to identify ``differentially-expressed genes" -- that is, genes
%whose mean expression (activity) level differs in two conditions. Here the ``effect" of interest is the difference in (log) 
%mean expression level between the two conditions, often referred to as the ``log-fold change". 
We begin with the simplest version of our method, and compare it with existing work, before detailing embellishments.

@@

This simple model features both the key ideas we want to emphasise in this paper: the UA is encapsulated in (\ref{eqn:mixnorm}) while
the different measurement precision of different observations is encapsulated in the likelihood (\ref{eqn:normlik}) -- specifically, observations
with larger standard error will have a flatter likelihood, and therefore have less impact on inference.
However, this simple model also has several additional assumptions that can be relaxed. Specifically,
\begin{enumerate}
\item  The use of a mixture of zero-mean normals (\ref{eqn:mixnorm}) also implies that $g$ is symmetric about 0; more flexibility can be obtained by replacing the mixture of normals with mixtures of uniforms [see (\ref{eqn:g-general})].
\item The model (\ref{eqn:beta}) assumes that the effects are identically distributed, independent of their standard errors $\shat$.
We can relax this to allow for a relationship between these quantities [see (\ref{eqn:beta-alpha})].
\item The likelihood (\ref{eqn:normlik}) effectively assumes that the number of observations used to compute $\bhat_j,\shat_j$ are sufficiently large to justify a normal approximation. We can generalize this likelihood using a $t$ likelihood [see (\ref{eqn:tlik})].
\end{enumerate}
Of course there remain limitations that are harder to relax, most notably the independence and conditional independence assumptions encapsulated in our model
(which are also made by most existing EB approaches to this problem). Correlations among tests certainly arise in practice, either due to genuine correlations
in the system of study, or due to unmeasured confounders, and their potential to impact results of an FDR analysis is important to consider
whatever analysis methods are used: see \cite{efron2007correlation,leek:2007} for relevant discussion.

@@

The usual EB approach to fitting this model would involve two simple steps:
\begin{enumerate}
\item Estimate the hyperparameters $\pi$ by maximizing the likelihood $L(\pi)$, given by (\ref{eqn:marginallik}), yielding $\hat{\pi} := \arg \max L(\pi)$.
\item Compute quantities of interest from the conditional distributions $p(\beta_j | \bhat, \shat, \hat{\pi})$. For example, the evidence
against the null hypothesis $\beta_j=0$ can be summarized by $p(\beta_j \neq 0 | | \bhat, \shat,\hat{\pi})$.
\end{enumerate}
Both steps 1 and 2 are very straightforward: $\hat{\pi}$ can be obtained using a simple EM algorithm \cite{dempster77}, and the conditional distributions $p(\beta_j | \bhat_j, \shat_j,\hat{\pi})$ are analytically available, each a mixture of a point mass on zero and $K$ normal distributions.
(Note that the simplicity of the EM algorithm in step 1 is due to our using a fixed grid for $\sigma_k$ in (\ref{eqn:mixnorm}), instead of estimating $\sigma_k$,
which may seem more natural but is not straightforward when $\shat_j$ varies among $j$. This simple device may be useful in other applications.)

@@

The lfdr, like most other measures of significance (e.g. $p$ values and $q$ values), is rooted in the hypothesis testing paradigm which focuses on 
whether or not an effect is exactly zero. This paradigm is popular, despite the fact that many statistical practitioners have argued that it is often inappropriate because
the null hypothesis $H_j: \beta_j=0$ is often implausible. For example, Tukey  (\cite{tukey1991philosophy}) argued that
``All we know about the world teaches us that the effects of $A$ and $B$ are always different -- in some decimal place -- for any $A$ and $B$. Thus asking `Are the effects different?' is foolish." Instead, Tukey suggested (\cite{tukey1962future}, p32,) that one should address
\begin{quote}
...the more meaningful question: ``is the evidence strong enough to support a belief that the observed difference has the correct sign?"
\end{quote}
Along the same lines, Gelman and co-authors \cite{gelman2000type, gelman2012we} suggest  
focussing on ``type S errors", meaning errors in sign, rather than the more traditional type I errors.

Motivated by these suggestions, we define the ``local False Sign Rate" for effect $j$, $\lfsr_j$, to be the probability that we
would make an error in the sign of effect $j$ if we were forced to declare it either positive or negative. Specifically,
\begin{equation} \label{eqn:lfsr}
\lfsr_j := \min[ p(\beta_j \geq 0| \bhat, s), p(\beta_j \leq 0| \hat\pi, \bhat, s) ].
\end{equation}
To illustrate, suppose for concreteness
that $p(\beta_j < 0| \bhat, s, \hat\pi))=0.95,  p(\beta_j =0| \bhat, s, \hat\pi)) = 0.03, p(\beta_j >0| \bhat, s, \hat\pi) = 0.02$. Then 
from (\ref{eqn:lfsr}) $\lfsr_j=\min(0.05,0.98)=0.05$ (and, from (\ref{eqn:fdr}), $\lfdr_j=0.03$). This $\lfsr$ corresponds to the fact that, given these results, 
our best guess for the sign of $\beta_j$ is that it is negative, and the probability that this guess is wrong would be $0.05$.

As our notation suggests, $\lfsr_j$ is intended to be compared and contrasted with $\lfdr_j$: whereas small values of $\lfdr_j$ indicate that we can be {\it confident that $\beta_j$ is non-zero}, 
small values of $\lfsr_j$ indicate that we can be {\it confident in the sign of $\beta_j$}. 
Of coure, being confident in the sign of an effect logically implies that we are confident it is non-zero, and
this is reflected in the fact that $\lfsr_j \geq \lfdr_j$ 
(this follows from the definition because both the events $\beta_j \geq 0$
and $\beta_j \leq 0$ in (\ref{eqn:lfsr}) include the event $\beta_j=0$).
In this sense, as a measure of ``significance", $\lfsr$ is more conservative than $\lfdr$. More importantly, as we illustrate in Section \ref{sec:lfsr},
$\lfsr$ can be substantially more robust to modelling assumptions than $\lfdr$.

@@

Among previous methods that explicitly consider the estimation of False Discovery Rates and related quantities,
our work here seems most naturally compared with the Empirical Bayes methods of \cite{efron2008microarrays} and \cite{muralidharan2010empirical}
 (implemented in the R packages \locfdr and \mixfdr respectively) and with the widely-used methods from  \cite{storey.03} (implemented in the R package \qvalue), which although not formally an EB approach, shares some elements in common.
  %Here we highlight the key differences between our approach and these three existing approaches.

There are two key differences between the approach implemented here and all of these three existing methods. First, 
whereas these existing methods summarize the information on $\beta_j$ by a single number -- either a $z$ score (\locfdr and \mixfdr), or a $p$ value (\qvalue) -- 
we instead work with two numbers ($\bhat_j,\shat_j$). Here we are building on \cite{wakefield:2009}, who develops Bayesian tests (Bayes Factors) for individual null hypotheses using these two numbers, using the normal approximation \ref{eqn:normlik}.
Using two numbers instead of one clearly has the potential to be more informative, and indeed,
as an example of this, Section \ref{good-poor-hist} illustrates how it can improve performance by taking better account of variation in measurement precision among observations.
(And in the special case where $\shat_j$ are equal for all $j$, our approach essentially comes down to the same thing as these existing methods.)
% Or more generally Section xx illustrates the potential practical effects

@@

Given that the UA and ZA are so different, it seems worth discussing why we favor the UA. 
Although the UA will not apply to all situations, we believe that it will often be reasonable, especially in FDR-related contexts
that have traditionally focussed on rejecting the null hypotheses $\beta_j=0$. This is because if ``$\beta_j=0$" is a plausible null hypothesis,  
it seems reasonable to expect that ``$\beta_j$ very near 0" is also plausible. Further, it seems reasonable to expect that larger effects become
decreasingly plausible, and so the distribution of the effects will be unimodal about 0. To paraphrase Tukey, ``All we know about the world teaches us that large effects are rare, whereas small effects abound."
We emphasise that the UA relates to the distribution of {\it all} effects, and not only the {\it detectable} effects (i.e.~those that are significantly different from zero). It is very likely that the distribution of {\it detectable} non-zero effects will be multimodal, with one mode for detectable positive effects and another for detectable negative effects, and the UA does not contradict this.

@@

Alternatively, we could motivate the UA by its effect on point estimates, which is to ``shrink" the estimates towards the mode - 
such shrinkage is desirable from several standpoints for improving estimation accuracy. Indeed most model-based approaches to shrinkage
make parametric assumptions that obey the UA (e.g. \cite{johnstone2004needles}).
Further, almost all analogous work in sparse regression models make the UA for the regression coefficents - 
common choices of uni-modal distribution being the spike and slab, Laplace, $t$, normal-gamma, normal-inverse-gamma, or horseshoe priors \cite{carvalho2010horseshoe}.
These are all less flexible than the approach we take here, which provides for general uni-modal distributions, and 
it may be fruitful to apply our methods to the regression context; indeed see \cite{moser:2015} for work in this vein. 
The UA assumption on regression coefficients is directly analagous to our UA for effects, and so we view its
widespread use in the regression context as supporting its use here.

In addition to these arguments, the UA also has a considerable practical benefit: it produces very simple procedures that are both computationally
and statistically stable. We illustrate these features in Results.

@@

There is also a very considerable literature that does not directly focus on the FDR problem, but which involves essentially the same models,
and deals with closely-related issues.  Among these, \cite{cordy1997deconvolution} is perhaps most similar to our work:
indeed all the elements of our approach outlined above, except for the point mass on 0 and corresponding penalty term, appear in their paper.
However, they focus entirely on the estimation of $g$, in contrast to our focus on estimating $\beta_j$; 
and they provide no software implementation.  More generally, the literature is too large to do a comprehensive review here, but relevant key-words include ``empirical bayes", ``shrinkage", ``deconvolution", ``semi-parametric", ``shape-constrained", and ``heteroskedastic". Some pointers to recent papers in which other relevant
citations can be found include \cite{xie2012sure, sarkar:2014, koenker2014convex}. Much (but not all) of the literature focusses on the homoskedastic case (i.e. $\shat_j$ all equal) whereas we allow for heteroskedasticity. And much (but not all) of the recent shrinkage-oriented literature focuses only on point estimation of $\beta_j$, whereas for FDR-related applications measures of uncertainty are essential. Several recent papers consider more flexible non-parametric assumptions on 
$g$ than the UA assumption we make here. In particular, \cite{jiang2009general,koenker2014convex} consider the unconstrained non-parametric maximum likelihood
estimate (NPMLE) for $g$. These methods may provide alternatives to our approach in settings where the UA assumption is considered too restrictive. However, the  NPMLE for $g$ is a discrete distribution, which will induce a discrete posterior distribution on $\beta_j$, and so although the NPMLE
may perform well for point estimation, it seems possible it will not adequately reflect uncertainty in $\beta_j$, and some regularization on $g$ may be necessary.

@@

\subsection*{Embellishments}

\subsection*{Implementation Details}

See Section \ref{sec:implement} for further implementation details.

@@

We compare results of \ashr with existing FDR-based methods implemented
in the R packages \qvalue (v1.99.1 from Bioconductor), \locfdr (v1.1-7 from \url{https://cran.r-project.org/src/contrib/Archive/locfdr/}), and \mixfdr (v1.0, from \url{https://cran.r-project.org/src/contrib/Archive/mixfdr/}).  In all our simulations we assume that the test statistics follow the expected theoretical distribution under the null, and we indicate this
to \locfdr using {\tt nulltype=0} and to \mixfdr using {\tt theonull=TRUE}. Otherwise all packages were used with default options.

@@

Here we consider the effects of making the UA. In this section, to isolate these effects we consider the simplest case, where every observation has the same
standard error, $s_j=1$ and all methods are provided that information. That is,
$\bhat_j | \beta_j \sim N(\beta_j,1)$ and $\shat_j=s_j=1$. In this case the $z$ scores $z_j:=\bhat_j/\shat_j=\bhat_j$, so modelling the $z$ scores is the same as modelling the $\bhat_j$, and so the only difference between our method and methods like $\locfdr$ and $\mixfdr$ are in how they estimate $g$.

To briefly summarize the results in this section:
\begin{enumerate}
\item The UA can produce very different inferences compared with the ZA.
\item The UA can yield conservative estimates of the proportion of true nulls, $\pi_0$, and hence conservative estimates of \lfdr and \FDR.
\item The UA results in a stable procedure, both numerically and statistically, and is somewhat robust to deviations from unimodality.
\end{enumerate}

@@

\begin{figure}
\center \includegraphics[height=6in]{Rcode/figures/decomp_ZA.pdf}
\caption{Comparison of the way that different methods decompose $p$ values (left) and $z$ scores (right) into a null component (dark blue) and an alternative component (light blue). In the $z$ score space the alternative distribution is placed on the bottom to highlight the differences in its shape among methods.
The three existing methods (\qvalue, \locfdr, \mixfdr) all effectively make the Zero Assumption, which results in a ``hole" in the alternative $z$ score distribution around 0.
In contrast the method introduced here (\ashr) assumes that the effect sizes (and thus the $z$ scores) have a unimodal distribution about 0, resulting in a very different decomposition. (In this case the \ashr decomposition is closer to the truth: the data were simulated under a model where all of the effects are non-zero -- specifically, $\beta_j \sim N(0,1)$, $s_j=1$, resulting in $z_j =\bhat_j\sim N(0,2)$ -- so the ``true" decomposition would make everything light blue.)} \label{fig:ZA}
\end{figure}

To illustrate the different inferences from the UA and ZA we show results for a single
dataset simulated with the true effects $\beta_j \sim N(0,1)$ (so with $s_j=1$, $\bhat_j  \sim N(0,2^2)$). We used each of the methods
\qvalue, \locfdr, \mixfdr and \ashr to decompose the $z$ scores ($z_j = \bhat_j$), or their corresponding $p$ values, into null and alternative components.
The results (Figure \ref{fig:ZA}) illustrate the clear difference between the existing methods and our method. The effects of the ZA made by \qvalue and \locfdr
are visually clear, producing a ``hole"  in the alternative $z$ score distribution around 0. Although \mixfdr does not formally make the ZA, its decomposition
exhibits a similar hole. In contrast, due to the UA, the alternative $z$ score distribution for \ashr is required to have a mode at 0, 
effectively ``filling in" the hole.  (Of course the null distribution also has a peak at 0, and the local fdr 
 under the UA is still smallest for $z$ scores that are far from zero -- i.e. large $z$ scores remain the ``most significant".)

>>>>

\def\lfdr{\textit{lfdr}}
\def\lfsr{\textit{lfsr}}
\def\x{\mbf{x}}
\def\y{\mbf{y}}
\def\e{\mbf{e}}
\def\g{\mbf{g}}
\def\p{p}
\def\Yb{\hat{Y}_1^{\text{BAYES}}}
\def\Xperp{X_{1 \perp 0}}
\def\Pperp{P_{1 \perp 0}}
\def\Pperpb{\Pperp^{\text{B}}}
\def \hatd { \widehat{ d } }
\def \dhatin {\hatd^{\mbox{\tiny IN}}}
\def \dhatsw {\hatd^{\mbox{\tiny SW}}}
\def \mvn{\text{MVN}}
\def\mn{\text{MN}}
\def \iw{\text{W}^{-1}}
\def \fp {fastPHASE\ }
\def\bhat{\hat{\beta}}
\def\shat{\hat{s}}
\def\var{\rm Var}
\def\mvr{\text{BMVR}}
\def\bfuni{\text{BF}_\text{uni}}
\def\one{\mbf{1}}
\def\zero{\mbf{0}}
\def\hall{H_{\text{all}}}
\def\pall{\p_{\text{all}}}
\def\bfall{\text{BF}_\text{all}}
\def\bfav{\text{BF}_\text{av}}
\def\gall{\gamma_\text{all}}
\def\limbfall{\bfall^\rightarrow}
\def\limbfav{\bfav^\rightarrow}
\def\limbfgamma{\BF_\gamma^\rightarrow}
\def\sxx{S_{xx}}
\def\syy{S_{yy}}
\def\vyy{V_{yy}}
\def\vyx{V_{yx}}
\def\vxx{{V_{xx}}}
\def\rss{\text{\rm RSS}}
\def\dss{\text{\rm $\Delta$SS}}
\def\U{U}
\def\D{D}
\def\I{I}
\def\luu{L_{UU}}
\def\indep{\perp}
\def\qvalue{{\tt qvalue}\xspace}
\def\locfdr{{\tt locfdr}\xspace}
\def\mixfdr{{\tt mixfdr}\xspace}
\def\ashr{{\tt ashr}\xspace}

@@

In addition to these two new ideas, we highlight a third idea that is old, but which remains under-used in practice:
the idea that it may be preferable to focus on estimation rather than on testing.
In principle, Bayesian approaches can naturally unify testing and estimation into a single framework -- testing is
simply estimation with some positive prior probability that the effect is exactly zero.
However, despite ongoing interest in this area from both frequentist \cite{benjamini2005false} and Bayesian \cite{zhao2012empirical,gelman2012we} 
perspectives, in practice large-scale studies that assess many effects almost invariably focus on testing significance and
controlling the FDR, and not on estimation. To help provide a bridge between FDR and estimation we introduce the term
``local false sign rate" (lfsr), which is analogous to the ``local false discovery rate" (\lfdr) \cite{efron2008microarrays}, but which measures confidence  
in the {\it sign} of each effect rather than confidence in each effect being non-zero. We show that in some settings, particularly those with many discoveries, 
the $\lfsr$ and $\lfdr$ can be quite different, and emphasise benefits of the lfsr, particularly its increased robustness to modelling assumptions.

@@

\def\df{df}
\def\FDR{\text{FDR}}
\def\fdr{\text{\lfdr}}
\def\FSR{\text{FSR}}
\def\fsr{\text{lfsr}}

@@

% Here we consider one setting in which FDR-based methods are widely used:
%an experimenter has measured a large numbers of ``effects", each with an associated
%measurement precision (standard error), 
%and the goal is to identify which of the effects we can declare to be non-zero, with some prescribed level of confidence.
%Although the usual focus of FDR-based methods is on distinguishing zero and non-zero effects,
%here we also focus on providing estimates -- both point estimates and interval estimates -- for these effects.
%This setting arises commonly in many areas of statistics, and particularly in genomics applications.
%For example, in genomics
%a common goal is to identify ``differentially-expressed genes" -- that is, genes
%whose mean expression (activity) level differs in two conditions. Here the ``effect" of interest is the difference in (log) 
%mean expression level between the two conditions, often referred to as the ``log-fold change". 
Here we describe the simplest version of our method, and briefly discuss embellishments we have also implemented.

@@

This simple model features both the key ideas we want to emphasise in this paper: the UA is encapsulated in (\ref{eqn:mixnorm}) while
the different measurement precision of different observations is encapsulated in the likelihood (\ref{eqn:normlik}) -- specifically, observations
with larger standard error will have a flatter likelihood, and therefore have less impact on inference.
However, this simple model also has several additional assumptions that can be relaxed. Specifically,
\begin{enumerate}
\item  The use of a mixture of zero-mean normals (\ref{eqn:mixnorm}) also implies that $g$ is symmetric about 0; more flexibility can be obtained by replacing the mixture of normals with mixtures of uniforms [see (\ref{eqn:g-general})].
\item The model (\ref{eqn:beta}) assumes that the effects are identically distributed, independent of their standard errors $\shat$.
We can relax this to allow for a relationship between these quantities [see (\ref{eqn:beta-alpha})].
\item The likelihood (\ref{eqn:normlik}) effectively assumes that the number of observations used to compute $\bhat_j,\shat_j$ are sufficiently large to justify a normal approximation. We can generalize this likelihood using a $t$ likelihood [see (\ref{eqn:tlik})].
\end{enumerate}
These embellishments are detailed in Embellishments and Implementation Details.
Of course there remain limitations that are harder to relax, most notably the independence and conditional independence assumptions encapsulated in our model
(which are also made by most existing EB approaches to this problem). Correlations among tests certainly arise in practice, either due to genuine correlations
in the system of study, or due to unmeasured confounders, and their potential to impact results of an FDR analysis is important to consider
whatever analysis methods are used: see \cite{efron2007correlation,leek:2007} for relevant discussion.

@@

The usual EB approach to fitting this model would involve two simple steps:
\begin{enumerate}
\item Estimate the hyperparameters $\pi$ by maximizing the likelihood $L(\pi)$, given by (\ref{eqn:marginallik}), yielding $\hat{\pi} := \arg \max L(\pi)$.
\item Compute quantities of interest from the conditional distributions $p(\beta_j | \bhat, \shat, \hat{\pi})$. For example, the evidence
against the null hypothesis $\beta_j=0$ can be summarized by $p(\beta_j \neq 0 | | \bhat, \shat,\hat{\pi})$.
\end{enumerate}
Both steps 1 and 2 are very straightforward: $\hat{\pi}$ can be obtained using a simple EM algorithm \cite{dempster77}, and the conditional distributions $p(\beta_j | \bhat_j, \shat_j,\hat{\pi})$ are analytically available, each a mixture of a point mass on zero and $K$ normal distributions.
(The simplicity of the EM algorithm in step 1 is due to our use of a fixed grid for $\sigma_k$ in (\ref{eqn:mixnorm}), instead of estimating $\sigma_k$,
which may seem more natural but is not straightforward when $\shat_j$ varies among $j$. This simple device may be useful in other applications.)

@@

The \lfdr, like most other measures of significance (e.g. $p$ values and $q$ values), is rooted in the hypothesis testing paradigm which focuses on 
whether or not an effect is exactly zero. This paradigm is popular, despite the fact that many statistical practitioners have argued that it is often inappropriate because
the null hypothesis $H_j: \beta_j=0$ is often implausible. For example, Tukey  (\cite{tukey1991philosophy}) argued that
``All we know about the world teaches us that the effects of $A$ and $B$ are always different -- in some decimal place -- for any $A$ and $B$. Thus asking `Are the effects different?' is foolish." Instead, Tukey suggested (\cite{tukey1962future}, p32,) that one should address
\begin{quote}
...the more meaningful question: ``is the evidence strong enough to support a belief that the observed difference has the correct sign?"
\end{quote}
Along the same lines, Gelman and co-authors \cite{gelman2000type, gelman2012we} suggest  
focussing on ``type S errors", meaning errors in sign, rather than the more traditional type I errors.

Motivated by these suggestions, we define the ``local False Sign Rate" for effect $j$, $\lfsr_j$, to be the probability that we
would make an error in the sign of effect $j$ if we were forced to declare it either positive or negative. Specifically,
\begin{equation} \label{eqn:lfsr}
\lfsr_j := \min[ p(\beta_j \geq 0| \bhat, s), p(\beta_j \leq 0| \hat\pi, \bhat, s) ].
\end{equation}
To illustrate, suppose that 
\begin{gather*}
p(\beta_j < 0| \bhat, s, \hat\pi)=0.95, \\
p(\beta_j =0| \bhat, s, \hat\pi) = 0.03, \\
p(\beta_j >0| \bhat, s, \hat\pi) = 0.02.
\end{gather*} 
Then 
from (\ref{eqn:lfsr}) $\lfsr_j=\min(0.05,0.98)=0.05$ (and, from (\ref{eqn:fdr}), $\lfdr_j=0.03$). This $\lfsr$ corresponds to the fact that, given these results, 
our best guess for the sign of $\beta_j$ is that it is negative, and the probability that this guess is wrong would be $0.05$.

As our notation suggests, $\lfsr_j$ is intended to be compared and contrasted with $\lfdr_j$: whereas small values of $\lfdr_j$ indicate that we can be {\it confident that $\beta_j$ is non-zero}, 
small values of $\lfsr_j$ indicate that we can be {\it confident in the sign of $\beta_j$}. 
Of coure, being confident in the sign of an effect logically implies that we are confident it is non-zero, and
this is reflected in the fact that $\lfsr_j \geq \lfdr_j$ 
(this follows from the definition because both the events $\beta_j \geq 0$
and $\beta_j \leq 0$ in (\ref{eqn:lfsr}) include the event $\beta_j=0$).
In this sense, as a measure of ``significance", $\lfsr$ is more conservative than $\lfdr$. More importantly, as we illustrate in Results,
$\lfsr$ can be substantially more robust to modelling assumptions than $\lfdr$.

@@

Among previous methods that explicitly consider the FDR and related quantities,
our work here seems most naturally compared with the EB methods of \cite{efron2008microarrays} and \cite{muralidharan2010empirical}
 (implemented in the R packages \locfdr and \mixfdr respectively) and with the widely-used methods from  \cite{storey.03} (implemented in the R package \qvalue), which although not formally an EB approach, shares some elements in common.
  %Here we highlight the key differences between our approach and these three existing approaches.

There are two key differences between our approach and all of these three existing methods. First, 
whereas these existing methods summarize the information on $\beta_j$ by a single number -- either a $z$ score (\locfdr and \mixfdr), or a $p$ value (\qvalue) -- 
we instead work with two numbers ($\bhat_j,\shat_j$). Here we are building on \cite{wakefield:2009}, who develops Bayesian tests 
for individual null hypotheses using these two numbers, using the normal approximation \ref{eqn:normlik}.
Using two numbers instead of one clearly has the potential to be more informative, and indeed, results later (Figure \ref{fig:goodpoor}) illustrate 
how it can improve performance by taking better account of variation in measurement precision among observations.
%(And in the special case where $\shat_j$ are equal for all $j$, our approach essentially comes down to the same thing as these existing methods.)
% Or more generally Section xx illustrates the potential practical effects

@@

Given that the UA and ZA are so different, it seems worth discussing why we generally favor the UA. 
Although the UA will not apply to all situations, we believe that it will often be reasonable, especially in FDR-related contexts
that have traditionally focussed on rejecting the null hypotheses $\beta_j=0$. This is because if ``$\beta_j=0$" is a plausible null hypothesis,  
it seems reasonable to expect that ``$\beta_j$ very near 0" is also plausible. Further, it seems reasonable to expect that larger effects become
decreasingly plausible, and so the distribution of the effects will be unimodal about 0. To paraphrase Tukey, ``All we know about the world teaches us that large effects are rare, whereas small effects abound."
We emphasise that the UA relates to the distribution of {\it all} effects, and not only the {\it detectable} effects (i.e.~those that are significantly different from zero). It is very likely that the distribution of {\it detectable} non-zero effects will be multimodal, with one mode for detectable positive effects and another for detectable negative effects, and the UA does not contradict this.

@@

In further support of the UA for FDR applications, we note that almost all analogous work in sparse regression models make the UA for the regression coefficents - 
common choices of uni-modal distribution being the spike and slab, Laplace, $t$, normal-gamma, normal-inverse-gamma, or horseshoe priors \cite{carvalho2010horseshoe}.
These are all less flexible than the approach we take here, which provides for general uni-modal distributions, and 
it may be fruitful to apply our methods to the regression context; indeed see \cite{moser:2015} for work in this vein. 
The UA assumption on regression coefficients is directly analagous to our UA here, and so its
widespread use in the regression context supports its use here.

Alternatively, we could motivate the UA by its effect on point estimates, which is to ``shrink" the estimates towards the mode - 
such shrinkage is desirable from several standpoints for improving estimation accuracy. Indeed most model-based approaches to shrinkage
make parametric assumptions that obey the UA (e.g. \cite{johnstone2004needles}).

Finally, the UA also has a considerable practical benefit: it yields simple algorithms that are both computationally
and statistically stable. We illustrate these features in Results.

@@

There is also a very considerable literature that does not directly focus on the FDR problem, but which involves similar ideas and methods. 
 Among these, a paper about deconvolution \cite{cordy1997deconvolution} is most similar, methodologically, to our work here:
indeed, this paper includes all the elements of our approach outlined above, except for the point mass on 0 and corresponding penalty term.
This said, the focus is very different: \cite{cordy1997deconvolution} focuses entirely on estimating $g$, whereas our primary focus is on estimating $\beta_j$.
Also, they provide no software implementation.  More generally, the related literature is too large to review comprehensively, but relevant key-words include ``empirical bayes", ``shrinkage", ``deconvolution", ``semi-parametric", ``shape-constrained", and ``heteroskedastic". Some pointers to recent papers in which other relevant
citations can be found include \cite{xie2012sure, sarkar:2014, koenker2014convex}. Much of the literature focusses on the homoskedastic case (i.e. $\shat_j$ all equal) whereas we allow for heteroskedasticity. And much of the recent shrinkage-oriented literature focuses only on point estimation of $\beta_j$, whereas for FDR-related applications measures of uncertainty are essential. Several recent papers consider more flexible non-parametric assumptions on 
$g$ than the UA assumption we make here. In particular, \cite{jiang2009general,koenker2014convex} consider the unconstrained non-parametric maximum likelihood
estimate (NPMLE) for $g$. These methods may provide alternatives to our approach in settings where the UA assumption is considered too restrictive. However, the  NPMLE for $g$ is a discrete distribution, which will induce a discrete posterior distribution on $\beta_j$, and so although the NPMLE
may perform well for point estimation, it seems possible it will not adequately reflect uncertainty in $\beta_j$, and some regularization on $g$ may be necessary.
Indeed, one way of thinking about the UA is as a way to regularize $g$.

@@

@@

We compare results of \ashr with existing FDR-based methods implemented
in the R packages \qvalue (v2.0 from Bioconductor), \locfdr (v1.1-7 from \url{https://cran.r-project.org/src/contrib/Archive/locfdr/}), and \mixfdr (v1.0, from \url{https://cran.r-project.org/src/contrib/Archive/mixfdr/}).  In all our simulations we assume that the test statistics follow the expected theoretical distribution under the null, and we indicate this
to \locfdr using {\tt nulltype=0} and to \mixfdr using {\tt theonull=TRUE}. Otherwise all packages were used with default options.

@@

Here we consider the effects of making the UA. To isolate these effects we consider the simplest case, where every observation has the same
standard error, $s_j=1$ and all methods are provided that information. That is,
$\bhat_j | \beta_j \sim N(\beta_j,1)$ and $\shat_j=s_j=1$. In this case the $z$ scores $z_j:=\bhat_j/\shat_j=\bhat_j$, so modelling the $z$ scores is the same as modelling the $\bhat_j$, and so the only difference between our method and methods like $\locfdr$ and $\mixfdr$ are in how they estimate $g$.

To briefly summarize the results in this section:
\begin{enumerate}
\item The UA can produce very different inferences compared with the ZA made by existing methods.
\item The UA can yield conservative estimates of the proportion of true nulls, $\pi_0$, and hence conservative estimates of $\lfdr$ and $\FDR$.
\item The UA results in a stable procedure, both numerically and statistically, and is somewhat robust to deviations from unimodality.
\end{enumerate}

@@

\begin{figure}
\center \includegraphics[height=6in]{figures/decomp_ZA.pdf}
\caption{Illustration that the unimodal assumption (UA) in \ashr can produce very different results from existing methods.
The figure shows, for a single simulated dataset, the way different methods decompose $p$ values (left) and $z$ scores (right) into a null component (dark blue) and an alternative component (cyan). In the $z$ score space the alternative distribution is placed on the bottom to highlight the differences in its shape among methods.
The three existing methods (\qvalue, \locfdr, \mixfdr) all effectively make the Zero Assumption, which results in a ``hole" in the alternative $z$ score distribution around 0.
In contrast the method introduced here (\ashr) makes the Unimodal Assumption -- that the effect sizes, and thus the $z$ scores, have a unimodal distribution about 0 -- which yields a very different decomposition. (In this case the \ashr decomposition is closer to the truth: the data were simulated under a model where all of the effects are non-zero, so the ``true" decomposition would make everything cyan.)} \label{fig:ZA}
\end{figure}
